The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-28 paper/paper.Rnw
Add comment

ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  mutate(pred_median = posterior_predict(mod_tracking) %>% colMedians()) %>%
  select(country, cum_diff, pred_median) %>%
  gather(cat, value, -country) %>%
  ggplot(aes(country, value, fill = cat)) +
  geom_col(position = "dodge") +
  coord_flip()
@

>>>>

ready_data_two %>%
  filter(!is.na(age_selection)) %>%
  mutate(pred_median = posterior_predict(mod_tracking) %>% colMedians()) %>%
  select(country, cum_diff, pred_median) %>%
  gather(cat, value, -country) %>%
  ggplot(aes(country, value, fill = cat)) +
  geom_col(position = "dodge") +
  coord_flip()

# See how these models explain for the 90/80/70 gaps.
@
